An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2024-02-27 poly-embed-journal/poly-embed-journal-camera-ready.tex
figure tweaks
Fixing bibtex warnings

\tikzstyle{cell}=[dashed,thick]
\tikzstyle{simplex}=[thick]
\newcommand{\tikzfigscale}{2.5}
\newcommand{\tikzfigscalepgf}{.45}
\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Rafael M. Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.  
%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021general}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\tikzstyle{cell}=[dashed,thick]
\tikzstyle{simplex}=[thick]
\newcommand{\tikzfigscale}{2.5}
\newcommand{\tikzfigscalepgf}{.75}
\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro\thanks{Work done while a student at University of Colorado Boulder} \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	Boston College\\
	Chestnut Hill, MA, USA
	\AND
	\name Rafael M. Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the min-max objective in the literature on adversarial prediction~\citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial,fathony2018consistent} is a special case of this construction when one unfolds the definition of the convex conjugate of $-\risk \ell$.
% reducing to  playing the role of their is a maximum of affine functions, and the conjugate takes the infimum (which is always attained) so $C = (-\risk \ell)^*$ used in the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} lines up with their min-max objective.  
%\raft{TODO: We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{TODO: Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}
%\jessie{If I understand the papers correctly, the cited works take a loss matrix (often for adversarial classification or prediction) and use the dual to obtain a consistent surrogate for the task, so it's just a specific application of this construction.}
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, which excludes polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \citep{abernethy2013efficient} and in connections between proper losses and mechanism design \citep{frongillo2014general,frongillo2021elicitation}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{plainnat}
\bibliography{diss,extra}
